Untitled

### 2017-07-13 LowUseLondon.Rmd
Addin stats
Added in some general stats about the data, and also included a few new LADs. Removed Islington until they give me proper data

test <-  ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
  group_by(Admin_ward_code) %>%
  summarise(LAD11NM = first(LAD11NM),
            MeanPrice = first(MeanPrice),
            WardLowUse = first(WardLowUse)) %>%
  group_by(LAD11NM) %>%
  summarise(totalLow = sum(MeanPrice*WardLowUse)/1e6,
            TotalEmpt = sum(WardLowUse))

@@

 ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG, RGN15NM=="London"), 
          filtermap = FALSE,
          title = "Map of London with all current data")
SaveFig("LondonCont.png")

>>>>

test <-  ls(pattern = "LON") %>% map_df(~eval(parse(text=.x))) %>%
  group_by(Admin_ward_code) %>%
  summarise(LAD11NM = first(LAD11NM),
            MeanPrice = first(MeanPrice),
            WardLowUse = first(WardLowUse)) %>%
  group_by(LAD11NM) %>%
  summarise(totalLow = sum(MeanPrice*WardLowUse)/1e6,
            TotalEmpt = sum(WardLowUse))

@@

 ls(pattern = "LON") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG, RGN15NM=="London"), 
          filtermap = FALSE,
          title = "Map of London with all current data")
SaveFig("LondonCont.png")

### 2017-07-13 PaperCode.Rmd
Addin stats
Added in some general stats about the data, and also included a few new LADs. Removed Islington until they give me proper data

@@

setwd(Functions)
list.files() %>% map(source)
```

@@

Cumbria
```{r}
setwd(file.path(RegionsComp, "Region North West"))

@@

Suffolk

@@

#Serparete in to the two LADS
CoastWaveDATA <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .))  %>%
  StructureData(., lowuse = c(5,6,13,14,16:18))

@@

@@

test <- wardnames %>% filter(grepl("Kensington", LAD11NM))

test <- EW2 %>% filter(LAD11NM == "Wandsworth")

@@

WandsworthDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
  group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
  arrange(`Ptc Wardname`) %>% 
  filter(!is.na(`Ptc Wardname`)) %>% 
  bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
              select(Admin_ward_code)) %>%
  mutate(LowUse = Empty) %>%
  SemiDataStructure

@@

MertonDATA <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
  filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home ) %>%
  SemiDataStructure

@@

KingstonDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
  arrange(X__1) %>% slice(1:16) %>%
  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
  SemiDataStructure

#TowerHamlets
TowerDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
  filter(!is.na(DiscClass)) %>%
  group_by(Ward, DiscClass) %>%
  summarise(count = n()) %>% ungroup %>%
  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
  slice(c(1:13, 15:17, 14, 18:20)) %>%
   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
  SemiDataStructure

@@

General Stats
```{r}

ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  summarise(LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T))

@@

#Plot stuff
```{r}
x <-bind_rows(SouthwarkLONDATA, TowerDATA, LambethLONDATA, CoLLONDATA) %>% MakeLeaflet

MakeLeaflet(IslingtonLONDATA)
```

@@

setwd(basewd)
#Boostrap each LAD
BootStrapRES <- ls(pattern = "DATA") %>% map(~{print(.x)
  DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000)})

saveRDS(BootStrapRES, file = "BootStrapRES.rds")

@@

```{r}
#Give the resulting list the name of each LAD
elementnames <- sub("DATA", "", ls(pattern = "DATA"))

names(BootStrapRES)<- elementnames

#Perform the t-test on the resulting lists
TtestRESgreater <-BootStrapRES %>% map(~ValueTtest(.x))
TtestREStwo.sided <-BootStrapRES %>% map(~ValueTtest(.x, alternative = "two.sided"))
#Tidy results of thejust the ttest
TtestRES2 <- TtestRESgreater %>% map_df(~.x$t.test %>% tidy) %>%
  mutate(LAD = elementnames,
         absdiff = TtestRES %>% map_dbl(~.x$absdiff),
         Percdiff = TtestRES %>% map_dbl(~.x$Percdiff))

@@

WardData <- ls(pattern = "DATA") %>%
  map_df(~eval(parse(text=.x)) %>%
           select(WardLowUsePerc) %>%
        mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
          summarise( maxPerc = max(WardLowUsePerc),
          minPerc = min(WardLowUsePerc),
          diffPerc = maxPerc-minPerc,
          LAD = sub("DATA", "", .x)))

@@

Combine1 <- left_join(ANOVARES, TtestRES2, by = "LAD" ) %>% bind_cols(skew)

#look at specific data
BootStrapRES$Redbridge %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
```

@@

Combine1 <- left_join(Combine1, WardData,by = "LAD" )

@@

#P.value is low if diff perc is over 5%
#Both southwark and Tower of london have concil flat renovation?
#Southwark the Aylesbury estate is being redeveloped maing emptyness much higher than expected
#The blackwall an cubitt are being redevleoped with the blackwall reach, some housing is empty others are still occupied demolishin has not occured
Combine1 %>% ggplot(.,aes(x= diffPerc, y = p.value.y)) + geom_point()

test <- Combine1 %>%
  select(LAD, p.value.y, absdiff , maxPerc, minPerc,diffPerc, skew)

>>>>

Islington should be removed and put back in when they send the correct data, it is giving a false negative

@@

setwd(Functions)
list.files() %>% map(source)

Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up/Figures"
```

@@

#Cumbria
```{r}
setwd(file.path(RegionsComp, "Region North West"))

@@

#Suffolk

@@

#Serparete in to the two LADS
# CoastWaveDATA <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
#   mutate(Exemption.type = Exemption.type %>% trimws %>%
#            make.names %>% 
#            gsub("\\.{2,}" , ".", .))  %>%
#   StructureData(., lowuse = c(5,6,13,14,16:18))

CoastSUFFDATA <- read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .))  %>%
  StructureData(.,c(5,6,11,12,14:16))

WaveneySUFFDATA <- read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .))  %>%
  StructureData(., lowuse = c(5,6,13,14,16:18))

#Cambridge
```{r}
EastCambsDATA <- read_excel("EC FOI 130 - DISC_FOI_0_3944413b.xlsx", sheet=1)[1:4] %>%
  StructureData()

#Brightong and Hove

setwd(file.path(RegionsComp, "Region South East"))
list.files()

BrightonDATA <- read_excel("Copy of Brighton and HoveDiscountsLSOA (4).xlsx", sheet=1)%>% .[,c(2,3:5)] %>%
  StructureData(lowuse = 2:8)

#MakeLeaflet(BrightonDATA)

@@

#MakeLeaflet(NewhamLONDATA)

@@

@@

WandsworthLONDDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
  group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
  arrange(`Ptc Wardname`) %>% 
  filter(!is.na(`Ptc Wardname`)) %>% 
  bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
              select(Admin_ward_code)) %>%
  mutate(LowUse = Empty) %>%
  SemiDataStructure

@@

MertonLONDATA <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
  filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home ) %>%
  SemiDataStructure

@@

KingstonLONDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
  arrange(X__1) %>% slice(1:16) %>%
  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
  SemiDataStructure

#TowerHamlets
TowerLONDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
  filter(!is.na(DiscClass)) %>%
  group_by(Ward, DiscClass) %>%
  summarise(count = n()) %>% ungroup %>%
  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
  slice(c(1:13, 15:17, 14, 18:20)) %>%
   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
  SemiDataStructure

@@

General Stats
#UK population

#number of LUPS and Total Homes
ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  summarise(
           TotalLads = length(unique(LAD11CD)),
           LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           PercHomes = Homes/sum(EW2$Homes),
           Population = sum(Pop, na.rm= T),
           Poperc = Population/sum(EW2$Pop))

#Percentage of EW LADS
length(ls(pattern = "DATA"))/(EW2$LAD11NM %>% unique %>% length())

@@

#Plot stuff
```{r}
x <-bind_rows(SouthwarkLONDATA, TowerDATA, LambethLONDATA, CoLLONDATA, NewhamLONDATA) %>% MakeLeaflet

#MakeLeaflet(SouthwarkLONDATA)

#testSouth <- DistribCompareBootstrapper(SouthwarkLONDATA, 1652, 1000)
testSouth %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

ValueTtest(test)

@@

setwd(basewd)
#Boostrap each LAD
elementnames <- sub("DATA", "", ls(pattern = "DATA"))

if(file.exists("BootStrapRES.rds")){
 #this sectio of code loads the old list and appends the new LADs

  BootStrapRES<- readRDS("BootStrapRES.rds")
  newLADsnames <- sub("DATA", "", ls(pattern = "DATA")) %>% 
  .[!(. %in% names(BootStrapRES))] 
  newLADs <- paste0(newLADsnames, "DATA")

    #only bootstrap if there is something to add.
    if(length(newLADsnames)>0){
       newLADsBoot <- newLADs  %>% map(~{print(.x)
          DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000)})  
          names(newLADsBoot) <- newLADsnames
          BootStrapRES <- c(BootStrapRES, newLADsBoot)
     }

 #re-roder the whole lot to be alphabetical
 BootStrapRES <- BootStrapRES [order(names(BootStrapRES))]

}else{
  #If the list is not found it bootstrapps all the LADs at once, beware this can take a long time

  BootStrapRES <- ls(pattern = "DATA") %>% map(~{print(.x)
  DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000)})
  #Give the resulting list the name of each LAD
  names(BootStrapRES)<- elementnames

}
#SAve the file or updated file with the additional elements
saveRDS(BootStrapRES, file = "BootStrapRES.rds")

elementnames<- names(BootStrapRES)

@@

#Perform the t-test on the resulting lists
TtestRESgreater <-BootStrapRES %>% map(~ValueTtest(.x))
TtestREStwo.sided <-BootStrapRES %>% map(~ValueTtest(.x, alternative = "two.sided"))
#Tidy results of thejust the ttest
TtestRES2 <- TtestRESgreater %>% map_df(~.x$t.test %>% tidy) %>%
  mutate(LAD = elementnames,
         absdiff = TtestRESgreater %>% map_dbl(~.x$absdiff),
         Percdiff = TtestRESgreater %>% map_dbl(~.x$Percdiff))

@@

WardData <- ls(pattern = "DATA") %>%
  map_df(~eval(parse(text=.x)) %>%
           select(WardLowUsePerc) %>%
        mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
          summarise( maxPerc = max(WardLowUsePerc, na.rm=TRUE),
          minPerc = min(WardLowUsePerc, na.rm=TRUE),
          diffPerc = maxPerc-minPerc,
          LAD = sub("DATA", "", .x)))

@@

Combine1 <- left_join(ANOVARES, TtestRES2, by = "LAD" ) %>% left_join(WardData,by = "LAD" ) %>% bind_cols(skew)

test <- BootStrapRES$CoastWave
#look at specific data
BootStrapRES$SouthwarkLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

Why are some areas with negative difference?

The max percentage of low use is 5%
There is the council estate renovation effect.
All the areas are Urban
Also check deprivation,

@@

@@

#P.value is low if diff perc is over 5%
#Both southwark and Tower of london have concil flat renovation?
#Southwark the Aylesbury estate is being redeveloped making emptyness much higher than expected
#The blackwall an cubitt are being redevleoped with the blackwall reach, some housing is empty others are still occupied demolishin has not occured
Combine1 %>% ggplot(.,aes(x= diffPerc, y = p.value.y)) + geom_point()

Combine1 %>% ggplot(.,aes(x= maxPerc, y = p.value.y)) + geom_point() +
  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")

#Boring doesn't show anything interesting
Combine1 %>% ggplot(.,aes(x= p.value.x, y = p.value.y, colour =diffPerc>5 )) + geom_point()

Combine1 %>% ggplot(.,aes(x= maxPerc, y = p.value.y, colour =absdiff>0 )) + geom_point()

test <- Combine1 %>%
  select(LAD,p.value.x, p.value.y, absdiff , maxPerc, minPerc,diffPerc, skew)
